Manuscript draft

### 2019-05-30 manuscript/manuscript draft.Rmd
update manuscript draft

*GPP* Gross primary productivity is generally thought to be highest in the tropics. Modelling of global terrestrial ecosystem GPP though upscaling and calibration of eddy flux measurements indicates a peak in GPP in the tropics, with the highest levels in tropical forests [@Beer2010; @Jung2011]. This is corroborated by analysis of site-level GPP measurements, which show a strong positive correlation between GPP and mean annual temperature (MAT) and mean annual precipitation (MAP) [@Luyssaert2007], with the highest GPP values reported in tropical forests. There is evidence that this increase is not linear: increases in GPP have been reported to saturate above 1500mm MAP [@Luyssaert2007] and 25$^\circ$C [@Larjavaara2012].

>>>>

*GPP* Gross primary productivity is generally thought to be highest in the tropics. Modelling of global terrestrial ecosystem GPP though upscaling and calibration of eddy flux measurements indicates a peak in GPP in the tropics, with the highest levels in tropical forests [@Beer2010; @Jung2011]. This is corroborated by analysis of site-level GPP measurements, which show a strong positive correlation between GPP and mean annual temperature (MAT) and mean annual precipitation (MAP) [@Luyssaert2007], with the highest GPP values reported in tropical forests. There is evidence that this increase is not linear: increases in GPP have been reported to saturate above 1500mm MAP [@Luyssaert2007] and 25$^\circ$C MAT [@Larjavaara2012].

*NPP* The influence of latitude on global patterns of NPP is less clear than that of GPP. Simova and Storch (2017) found that, as with GPP, NPP decreases with latitude, peaking in the tropics. However, other studies have found the highest values of NPP in temperate forests, with increases in NPP saturating at 1500mm MAP and 10$^\circ$C MAT [@Luyssaert2007].

Primary productivity of forests is influenced by a range of factors. On a local scale, stand age [@Litton2007; @Gillman2015], management [@Simova2017]; nutrient availability [cite]; and altitude [@Girardin2010; @Malhi2017] all impact stand productivity. On a global scale, changes are likely to be influenced by climatic variables. The majority of studies to date have focused on the influence of MAP and MAT on productivity. While MAP and MAT have been argued to be significant predictors of productivity [@Chu2016], other studies have found that the correlation between productivity and MAT is a factor of the relationship between productivity and growing season length [@Kerkhoff2005; @Malhi2012; @Michaletz2014; @Michaletz2018].
